Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-01-05 Ben_Manuscripts/structure_paper/supplemental.tex
Minor edits to draft and additions to supplemental information

  \graphicspath{{./figures/}}  % put all the figures here
  \maketitle

  \begingroup
	\fontsize{14pt}{12pt}\selectfont
	\textbf{Further details regarding monomer parameterization}
  \endgroup

  Monomers were parameterized according to the following procedure:
  %BJC: need references
  \begin{enumerate}
	\item Create monomer structure file with connectivity : We drew atomistic
        structures using MarvinSketch 17.13. We optimized the 3D geometry of
	the structure using the 'Clean in 3D' function of MarvinSketch 17.13. 
        We saved the structure as a .mol file, then converted it to .pdb
	format using Open Babel 2.4.1. 
	\item Assign GAFF atomtypes using \texttt{antechamber} : Using the .pdb
	structure file as input, we ran \texttt{antechamber} using the AM1-BCC charge
	model. The net charge on the monomer is input as -1 since the sodium ion will
	be kept as a separate residue. The output of \texttt{antechamber} is used to
	create Amber topology files with \texttt{LEaP}. A detailed tutorial can be
	accessed elsewhere (http://ambermd.org/tutorials/basic/tutorial4b/) 
	\item Create gromacs topologies from Amber output : \texttt{LEaP}
	outputs a .inpcrd and a .prmtop file which are Amber topologies. Using
	acpype.py, we convert the \texttt{LEaP} output into GROMACS .gro and .top
	files. 
  \end{enumerate}

@@

\end{document}

>>>>

  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}  % put all the figures here
  \maketitle

  \noindent
  \begingroup
	\fontsize{14pt}{14pt}\selectfont
	\textbf{Further details regarding monomer parameterization} 
  \endgroup

  \vspace{1em}
  Monomers were parameterized according to the following procedure:
  \begin{enumerate}
	\item \textit{Create monomer structure file with connectivity} : We
	drew atomistic structures using MarvinSketch 17.13 with all hydrogen atoms
	drawn out explicitly. We optimized the 3D geometry of the structure using the
	'Clean in 3D' function of MarvinSketch 17.13~\cite{chemaxon_marvinsketch_2017}.
	We saved the structure as a .mol file, then converted it to .pdb format using
	Open Babel 2.4.1 \cite{oboyle_open_2011,noauthor_open_nodate}. 
	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using the .pdb
	structure file as input, we ran \texttt{antechamber}~\cite{wang_automatic_2006}
	using the AM1-BCC charge model. The net charge on the monomer is input as -1
	since the sodium ion will be kept as a separate residue. The output of
	\texttt{antechamber} is used to create Amber topology files with
	\texttt{LEaP}~\cite{case_ambertools16_2016}. A detailed tutorial can be accessed
	elsewhere \cite{walker_antechamber_nodate}.
	\item \textit{Create gromacs topologies from Amber output} : \texttt{LEaP}
	outputs a .inpcrd and a .prmtop file which are Amber topology files. Using
	acpype.py \cite{sousa_da_silva_acpype_2012}, we convert the \texttt{LEaP}
	output into GROMACS .gro and .top files. 
	\item \textit{Perform a simulated annealing procedure on the monomer} :
	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
	editconf}. The monomer was centered in the monomer in the box with edges of the
	box at least 3 nm from the monomer on all sides. We ran an energy minimzation
	on the system with the steepest descent algorithm.  Next we performed an NVT
	simulated annealing procedure. We linearly decreased the temperature of the
	system from 1000K to 50K over the course of 10 ns. We randomly chose a monomer
	configuration from the last 10 \% of the trajectory. 
	\item \textit{Reassign charges with \texttt{molcharge}}: With the monomer
	configuration taken from the annealed trajectory, we reassigned charges using
	\texttt{molcharge} using the am1bccsym method in order to ensure charges 
	are symmetric. This condition is not guaranteed with \texttt{antechamber}. 
	The charges in the gromacs topology file (.top) were replaced with the 
	new charges calculated by \texttt{molcharge}. 
	\item \textit{Anneal again to get final structure} : The same simulated
	annealing process was repeated using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from
	the last 10 \% of the trajectory and was used to build all assemblies
	reported (Figure~\ref{fig:monomer}).
  \end{enumerate}

@@

\bibliography{llc.bib}
\end{document}
